---
title: "ready4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ready4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, results='hide', message=FALSE, warning=F}
library(ready4)
```

## Motivation
Health economic models should ideally be both "living" ( kept up to date) and "transferable" (easy to selectively modify so they can be validly used in a new context). Research studies that use such models should be reproducible. These goals [can be hard to achieve in practice](https://www.ready4-dev.com/docs/getting-started/motivation/).

## Implementation
The `ready4` R library provides bare bones foundational elements of a [prototype software framework](https://rdcu.be/dIv8g) to: (i) develop living and transferable health economic models; and (ii) apply those models to implement reproducible health economic analyses. The framework is extended by multiple other R packages - see the framework's [project website](https://www.ready4-dev.com/) for details. 

## Use
For most users, the main applications of the ready4 library will be to:

- [find themed collections of health economic model modules that have been developed with the ready4 framework](V_04.html);

- [itemise available model modules and sub-modules and find examples of how to use them](V_05.html); and

- [apply these modules to undertake health economic analyses using a simple and consistent syntax](V_02.html).

For the above purposes, the ready4 library will be typically used in conjunction with the [ready4use](https://ready4-dev.github.io/ready4use/) and [ready4show](https://ready4-dev.github.io/ready4show/) libraries.

For users with software development expertise, the ready4 library also provides:

- [a template model module](V_01.html) that facilitates modular implementations of health economic models using an [object-oriented paradigm](V_03.html);

- [a simple programming syntax to make available to end-users](V_07.html); and

- [tools to partially automate the maintenance of an open source modelling project's website](V_06.html).

Developers that wish to author health economic models as R libraries with ready4 may wish to consider using the [ready4pack](https://ready4-dev.github.io/ready4pack/) library. However, that library (along with its two primary dependencies [ready4fun](https://ready4-dev.github.io/ready4fun/) and [ready4class](https://ready4-dev.github.io/ready4class/)) is not yet well documented and the ready4 framework remains a prototype. It is therefore recommended to [first contact the package authors](https://mph-economist.netlify.app/#contact) before undertaking R library development with ready4. 

## Further reading

- A [pre-print manuscript](https://arxiv.org/pdf/2403.17798) discussing the need for health economic models to be transparent, reusable and updatable;

- An 2024 [article in Pharmacoeconomics](https://rdcu.be/dIv8g) describing the ready4 prototype software framework;

- The [ready4 prototype software framework website](https://www.ready4-dev.com/);

- The [project website of the readyforwhatsnext model](https://readyforwhatsnext.org/) that is being developed with the ready4 software framework; and

- A [pre-print manuscript](https://www.medrxiv.org/content/10.1101/2021.07.07.21260129v4) describing a utility mapping study implemented with modules of the readyforwhatsnext model.
