---
title: "ready4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ready4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, results='hide', message=FALSE, warning=F}
library(ready4)
```

## Motivation
The social, economic and service systems that shape population health are complex and thus can be challenging to model. Some health economic modelling projects may therefore be more tractable if broken into smaller tasks and advanced by multiple teams. Such phased and collaborative approaches can be facilitated by use of common frameworks for the development of computational models that are both open and modular.

## Implementation
The `ready4` package provides bare bones foundational elements of a software framework to implement transparent, reusable and updatable computational health economic models in R. The framework is extended by multiple other R packages - see the [project documentation website](https://www.ready4-dev.com/) for details. 

### Articles
The `ready4` package includes model module templates, a simple programming syntax and helper functions that can be useful for health economic modelling. These concepts are discussed in the following articles:

- [Implement Modular Computational Health Economic Models](V_01.html)

- [Use A Simple And Consistent Syntax In Computational Health Economic Models](V_02.html)

- [Apply An Object-Oriented Paradigm To Computational Health Economic Models](V_03.html)

