---
title: "ready4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ready4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ready4)
```

## Motivation
The social, economic and service systems that shape population mental health are complex and thus can be challenging to model. Some mental health systems modelling projects may therefore be more tractable if broken into smaller tasks and advanced by multiple teams. Such phased and collaborative approaches can be facilitated by use of common frameworks for the development of computational models that are both open and modular.

The `ready4` package provides a bare bones initial outline of a framework for open science computational models of mental health systems. This initial framework is extended by multiple other R packages. The following vignette articles introduce the `ready4` framework and provide details of how the framework has been extended and applied:

- [Develop Modular Computational Models Of Mental Health Systems](V_01.html)

- [Use A Simple And Consistent Syntax In Computational Models Of Mental Health Systems](V_02.html)

- [Apply An Object-Oriented Paradigm To Developing Computational Models Of Mental Health Systems](V_03.html)

- [Find And Author Extensions To The Ready4 Framework](V_041.html)
