---
title: "Extending The Ready4 Framework"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extending The Ready4 Framework}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r}
library("ready4") 
```

The `ready4` package provides a "bare-bones" framework that is designed to be extended by other work. This vignette briefly summarises some examples of current extensions to the framework.

## R packages
A table of the most up to date list of R packages that extend the `ready4` framework can be generated using the `make_pkg_extensions_tb` function.

```{r warning=FALSE, message=FALSE}
x <- make_pkg_extensions_tb()
```

A HTML version of the table can be printed using `print_pkg_extensions`.

```{r warning=FALSE, message=FALSE}
print_pkg_extensions(x)
```

## Classes that extend ready4
A table of the modules (S4 classes) and sub-modules (S3 classes) that extend the parent classes shipped with `ready4` can be generated using `make_modules_tb`.

```{r warning=FALSE, message=FALSE}
y <- make_modules_tb(x)
```

HTML versions of the table can be printed using the `print_modules` function.

### Modules (S4 Classes)

```{r }
print_modules(y,
              what_1L_chr = "S4")

```

### Sub-modules (S3 Classes)
```{r }
print_modules(y,
              what_1L_chr = "S3")

```







