---
title: "Use A Simple And Consistent Syntax In Computational Health Economic Models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use A Simple And Consistent Syntax In Computational Health Economic Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```
```{r results='hide', message=FALSE, warning=F}
library(ready4) 
```

## Motivation
Transparency is one of the underpinning principles of ethical modelling practice. One way to improve the transparency of computational health economic models (such as those we are developing [in youth mental health](https://readyforwhatsnext.org)) is to ensure that the [programs implementing model analyses](https://readyforwhatsnext.org/docs/model/analyses/) can be meaningfully inspected by readers with different levels of technical expertise. Even non-technical readers should be able to follow the high-level logic implemented by model algorithms. If multiple analysis programs are written using a common simplified syntax then reviewers of those programs need to contend with relatively fewer new concepts. 

## Implementation
`ready4` provides a simple syntax that can be consistently applied to attach algorithms (methods) to [model modules](https://www.ready4-dev.com/docs/framework/implementation/modularity/). It does so by taking advantage of the [abstraction and polymorphism features of Object Oriented Programing](https://www.ready4-dev.com/docs/framework/implementation/paradigm/object-oriented/#transparent-computational-models) and R's use of generic functions. Generic functions don't implement algorithms themselves - their most salient features are a name and a high level description of the type of task that any method associated with that generic should perform. Whenever a developer creates a method for [classes that use R's S4 and S3 systems (the types used for model modules and sub-modules)](https://www.ready4-dev.com/docs/framework/implementation/modularity/#implementation), they can associate that method with the generic that has a description that is the best match for the algorithm being implemented.

### Available generics
A table that summarises the latest `ready4` syntax can be ingested from a periodically updated database using `get_methods_tb`.

```{r echo=FALSE}
# Not run
# x <- make_methods_tb()
```
```{r}
x <- get_methods_tb()
```

#### Core generics
`ready4` includes a number of core generic functions which describe the main types of method to be implemented by model modules. Notably, the `ready4` package does not associate methods with any of these core generics. Instead, methods are associated with these generics in [R packages of model modules](https://readyforwhatsnext.org/docs/tutorials/finding/libraries/). A HTML table of `ready4`'s  core generics and examples of methods associated with each generic can be displayed using the `print_methods` function, using the `return_1L_chr = "core"` argument. 

```{r}
print_methods(x,
              return_1L_chr = "core",
              scroll_width_1L_chr = "100%") 
```

#### Slot generics and methods
Each of the "core" generics also has a "slot" version, for use when applying a core method to a specified slot of a class. The `ready4` package associated methods for each of these "slot" generics for [the `Ready4Module` template](https://www.ready4-dev.com/docs/framework/implementation/modularity/#implementation). Two of these "slot" methods can also be used for additional purposes:

 - [procureSlot](https://ready4-dev.github.io/ready4/reference/procureSlot-methods.html) is a "getter" method - its default behaviour is to return the value of a specified slot. If the argument `use_procure_mthd_1L_lgl = T` is included in the method call, `procureSlot` will instead apply the `procure` method to a specified slot.
 
 - [renewSlot](https://ready4-dev.github.io/ready4/reference/procureSlot-methods.html) is a "setter" method - if any value other than "use_renew_mthd" (the default) is passed to the `new_val_xx` argument, that value will be assigned to the specified slot.
 
A HTML table of the slot generics bundled with `ready4` can be displayed using the `print_methods` function, using the `return_1L_chr = "slot"` argument.

```{r}
print_methods(x,
              return_1L_chr = "slot",
              scroll_width_1L_chr = "100%")
```

#### Extended `author` generics
Finally, there are a small number of other generics that are more general extensions of the core functions. Currently, these extended generics are all variants on the `author` generics, with each one specifying the type of output to be authored by the method. The `ready4` package does not include methods for any of these extended generics. A HTML table of the extended generics bundled with `ready4` can be displayed using the `print_methods` function, using the `return_1L_chr = "extended"` argument.

```{r}
print_methods(x,
              exclude_mthds_for_chr = "Ready4Module",
              return_1L_chr = "extended",
              scroll_width_1L_chr = "100%")
```

