---
title: "Make Computational Models Of Mental Health Systems More Transparent By Using A Simple And Consistent Syntax"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Make Computational Models Of Mental Health Systems More Transparent By Using A Simple And Consistent Syntax}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r results='hide', message=FALSE}
library("ready4") 
```
```{r echo=F}
# get_fn_descs <- function(fn_nms_chr = NULL,
#                          functions_tb = NULL,
#                          gh_repo_1L_chr = "ready4-dev/ready4",
#                          gh_tag_1L_chr = "Documentation_0.0",
#                          return_1L_chr = "all"){
#   if(is.null(functions_tb))
#     functions_tb <- get_functions_tb(gh_repo_1L_chr = gh_repo_1L_chr,
#                              gh_tag_1L_chr = gh_tag_1L_chr,
#                              return_1L_chr = return_1L_chr)
#   if(is.null(fn_nms_chr)){
#         fn_descs_chr <- functions_tb$fn_type_desc_chr
#   }else{
#       fn_descs_chr <- purrr::map_chr(fn_nms_chr,
#                                  ~get_from_lup_obj(functions_tb,
#                                                    match_value_xx = .x,
#                                                    match_var_nm_1L_chr = "fn_type_nm_chr",               
#                                                    target_var_nm_1L_chr = "fn_type_desc_chr"))
#   }
#   return(fn_descs_chr)
# }
# NEED TO DEPRECATE GET_MTHD_TITLE IN READY4FUN

```

## Motivation
Transparency is one of the underpinning principles of open science. One way to improve the transparency of computational models of mental health systems is to ensure that the programs implementing these models can be meaningfully inspected by readers of different level of technical expertise. Even non-technical readers should be able to follow the high-level logic implemented by model algorithms. Consistent use of simple programming syntax ing the main program implementing an analysis can help ensure that readers need contend with relatively new concepts when reviewing the code. 

## Implementation
`ready4` provides a simple syntax that can be consistently applied across multiple types of mental health computational modelling projects. It does so by taking advantage of the [polymorphism and abstraction features of Object Oriented Programing](V_03.html) and R's use of generic functions for [S4 and S3 classes (the types used for ready4 framework modules and sub-modules)](V_01.html).

## Finding ready4 Framework Methods

```{r warning=F}
x <- make_methods_tb()
```
### Core methods
```{r}
print_methods(x,
              return_1L_chr = "core")
```

### Slot methods

```{r}
print_methods(x,
              return_1L_chr = "slot")
```

### Extended `author` methods

```{r}
print_methods(x,
              exclude_mthds_for_chr = "Ready4Module",
              return_1L_chr = "extended")
```

## Ready4Module Methods

```{r}
get_methods()
```
