---
title: "Find And Author Extensions To The Ready4 Framework"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Find And Author Extensions To The Ready4 Framework}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r message=FALSE}
library("ready4") 
```

## Motivation
The `ready4` package provides a "bare-bones" framework that is designed to be extended by other work. This vignette briefly summarises some examples of current extensions to the framework.

```{r echo=FALSE}
## NETWORK EFFECTS
## CODE LIBRARIES
## DATASETS
## PROGRAMS
## BROCHURE
```

## Finding code libraries that extend the `ready4` framework
A table of the most up to date list of R package extensions to the `ready4` framework can be generated using the `make_pkg_extensions_tb` function.

```{r warning=FALSE, message=FALSE}
x <- make_pkg_extensions_tb()
```

A HTML version of the table can be printed using `print_pkg_extensions`.

```{r warning=FALSE, message=FALSE}
print_packages(x) 
```

## Authoring code libraries to extend the `ready4` framework
As `ready4` provides a framework for modular development of computational models of mental health systems, developers of framework extensions are expected to adopt a common set of standards. A [standardised workflow for authoring code libraries (R packages) that extend the ready4 framework](https://ready4-dev.github.io/ready4pack/articles/V_01.html) is supported by the [ready4pack package](https://ready4-dev.github.io/ready4pack/index.html).

```{r echo=FALSE}
## DATASETS
## PROGRAMS
```

## Finding datasets created with the `ready4` framework

```{r}
y <- get_dvs()
```
```{r}
print_dvs(y)
```

```{r}
print_dss(y,
          what_1L_chr = "real")
```

```{r}
print_dss(y,
          what_1L_chr = "fakes")
```

## Finding programs that illustrate the `ready4` framework
```{r}
print_vignettes(x)
```






