---
title: "Finding Applied Examples of Ready4 Modules and Sub-modules"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Finding Applied Examples of Ready4 Modules and Sub-modules}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r message=FALSE, warning=FALSE}
library(ready4)
```

## Motivation
When considering whether to use model modules, model developers and users will often want to see examples of each module's application The `ready4` package includes tools to allow a modelling project's maintainers to perform automated searches for vignette examples of model modules and to output tabular summaries of these modules that are suitable for inclusion on documentation website pages.

## Implementation

Details of how to search for themed collections of modules is described in [another article](https://readyforwhatsnext.org/docs/tutorials/finding/libraries/). A table itemising individual model modules and sub-modules authored with `ready4` can be generated using `make_modules_tb`. This function scrapes relevant data from the websites of module libraries that have been developed within a specified project's GitHub organisation and may take a couple of minutes to execute. In this example, we are going to examine modules from a [youth mental health model](https://readyforwhatsnext.org/).


```{r}
modules_tb <-  make_modules_tb(gh_repo_1L_chr = "ready4-dev/ready4")
```


A slightly quicker method to achieve a similar result is to use the `get_modules_tb` function. This function retrieves an archived version (and therefore potentially less up to date) of the modules summary table.


```{r eval=FALSE}
# Not run
# modules_tb <- get_modules_tb(gh_repo_1L_chr = "ready4-dev/ready4")
```


The `modules_tb` object itemises both ready4 modules (which always use R's "S4" class type) and sub-modules ("S3" class type). To display a HTML summary of just ready4 modules, you can use the `print_modules` function. 


```{r eval=FALSE}
print_modules(modules_tb, what_1L_chr = "S4")
```


```{r echo=FALSE}
print_modules(modules_tb, what_1L_chr = "S4")
```

You can use the same function to display only ready4 sub-modules.


```{r eval=FALSE}
print_modules(modules_tb, what_1L_chr = "S3")
```


```{r echo=FALSE}
print_modules(modules_tb, what_1L_chr = "S3")
```

